Scholten Read Sanborn

### 2015-11-13 shinyapps/scholtenReadSanborn2014.Rmd
start on interval model

```{r, echo=FALSE}
exp_disfac <- function(ssamt, sstime, llamt, lltime) {
  (ssamt/llamt)^(1/(lltime - sstime))
}

```{r, echo=FALSE}
inputPanel(
  sliderInput("ssamt", "Smaller Sooner $", min=0, max = 500, step=5, value= 10),
    sliderInput("llamt", "Larger Later $", min=0, max = 500, step=5, value= 20),
  sliderInput("sstime", "Smaller Sooner time", min=0, max = 365, step=1, value= 1),
    sliderInput("lltime", "Larger Later time", min=0, max = 365, step=1, value= 2)

  )

renderPrint({
exp_disfac(input$ssamt, input$sstime, input$llamt, input$lltime)

@@

>>>>

```{r, echo=FALSE}
exp_disfac <- function(ssamt, sstime, llamt, lltime) {
  (ssamt/llamt)^(1/(lltime - sstime))
}
```

```{r, echo=FALSE}
inputPanel(
  sliderInput("ssamt", "Smaller Sooner $", min=0, max = 500, step=5, value= 10),
  sliderInput("llamt", "Larger Later $", min=0, max = 500, step=5, value= 20),
  sliderInput("sstime", "Smaller Sooner time", min=0, max = 365, step=1, value= 1),
  sliderInput("lltime", "Larger Later time", min=0, max = 365, step=1, value= 2)
  )

renderPrint({
exp_disfac(input$ssamt, input$sstime, input$llamt, input$lltime) 
})
```

@@

## The interval discounting model: A hybrid evaluation rule

uses the value function hyperbolic

Interval discount function:

$$D(t_S, t_L) = (1 + \alpha (\frac{w(t_L) - w(t_S)}{\vartheta})^{\vartheta})^{-\beta/\alpha}$$

```{r}
w_t <- function (t, tau) {
  t <- as.numeric(t)
  tau <- as.numeric(tau)
  (1/tau) * log(1 + tau*t)
}

int_fn <- function(sstime, lltime, alpha, theta, beta, tau) {

  sstime <- as.numeric(sstime)
  lltime <- as.numeric(lltime)
  alpha <- as.numeric(alpha)
  theta <- as.numeric(theta)
  beta <- as.numeric(beta)

  (1 + alpha * ((w_t(lltime) - w_t(sstime))/theta)^theta) ^(-beta/alpha)
}

int_df <- data.frame(int_len = 0:100)

int_df1 <- int_df %>%
  mutate(sstime =,
         lltime,
         alpha,
         theta,
         beta)

```{r, echo=FALSE}
inputPanel(
  textInput("inton", "Interval onset"),
  textInput("intlen", "Larger Later time"),
  textInput("beta", "beta > 0 delay"),
  textInput("tau", "tau > departure from exponential discounting")
  )
